From Reversible Programs to \\ Univalent Universes and Back

### 2017-06-26 upi.tex
code

{\small
\[\def\arraystretch{1.2}\begin{array}{rcl}
\AgdaFunction{toffoli} &:& \bt \otimes (\bt \otimes \bt)
                           \leftrightarrow  \bt \otimes (\bt \otimes \bt) \\
\AgdaFunction{toffoli} &=&
      \bt \otimes (\bt \otimes \bt) \\
&& \qquad\byiso{\AgdaFunction{unfoldBool} \otimes \AgdaFunction{id}} \\
&& (\ot \oplus \ot) \otimes (\bt \otimes \bt) \\
&& \qquad\byiso{\AgdaFunction{dist}} \\
&& (\ot \otimes (\bt \otimes \bt)) \oplus (\ot \otimes (\bt \otimes \bt)) \\
&& \qquad\byiso{\AgdaFunction{id} \oplus (\AgdaFunction{id} \otimes \AgdaFunction{cnot})} \\
&& (\ot \otimes (\bt \otimes \bt)) \oplus (\ot \otimes (\bt \otimes \bt)) \\
&& \qquad\byiso{\AgdaFunction{factor}} \\
&& (\ot \oplus \ot) \otimes (\bt \otimes \bt) \\
&& \qquad\byiso{\AgdaFunction{foldBool} \otimes \AgdaFunction{id}} \\
&& \bt \otimes (\bt \otimes \bt)
\end{array}\]}

>>>>

{\small
\[\def\arraystretch{1.2}\begin{array}{rcl}
\AgdaFunction{controlled} &:& (a \leftrightarrow a) \rightarrow 
                              \bt \otimes a \leftrightarrow \bt \otimes a \\
\AgdaFunction{controlled}~\AgdaFunction{f} &=& 
      \bt \otimes a \\
&& \qquad\byiso{\AgdaFunction{unfoldBool} \otimes \AgdaFunction{id}} \\
&& (\ot \oplus \ot) \otimes a \\
&& \qquad\byiso{\AgdaFunction{dist}} \\
&& (\ot \otimes a) \oplus (\ot \otimes a) \\
&& \qquad\byiso{\AgdaFunction{id} \oplus (\AgdaFunction{id} \otimes \AgdaFunction{f})} \\
&& (\ot \otimes a) \oplus (\ot \otimes a) \\
&& \qquad\byiso{\AgdaFunction{factor}} \\
&& (\ot \oplus \ot) \otimes a \\
&& \qquad\byiso{\AgdaFunction{foldBool} \otimes \AgdaFunction{id}} \\
&& \bt \otimes a \\
\\ 
\AgdaFunction{not} &:& \bt \leftrightarrow \bt \\
\AgdaFunction{not} &=& 
  \AgdaFunction{unfoldBool} \odot \AgdaFunction{swap₊} \odot \AgdaFunction{foldBool} \\
\\ 
\AgdaFunction{cnot} &:& \bt \otimes \bt \leftrightarrow \bt \otimes \bt \\
\AgdaFunction{cnot} &=& \AgdaFunction{controlled}~\AgdaFunction{not} \\
\\ 
\AgdaFunction{toffoli} &:& \bt \otimes (\bt \otimes \bt)
                           \leftrightarrow  \bt \otimes (\bt \otimes \bt) \\
\AgdaFunction{toffoli} &=& \AgdaFunction{controlled}~\AgdaFunction{cnot}
\end{array}\]}
